Mortality Trend Among Shelter Residents: Closely Tied To Virus Outbreaks

### 2024-09-27 paper/paper.qmd
Made change to the coding style using styler

---
title: "Trends in Mortality Among Shelter Residents: : Closely Tied To Virus Outbreaks"
subtitle: "Analyzing period: 2007 to 2024"
author: 
  - Mandy He
thanks: "Code and data are available at: https://open.toronto.ca/dataset/deaths-of-shelter-residents/"
date: Septmeber 27 2024
date-format: long
abstract: "Homelessness remain pressing issues in today’s society, particularly evident in downtown Toronto, due to  harsh living conditions, these individuals often face severe health issues, leading to an increased risk of mortality. This paper analyzes the trends in mortality rates among shelter residents in the City of Toronto from 2007 to 2024, highlighting patterns over time and exploring the factors contributing to these rates. This paper found that the trend in the mortality rate of this minority group reflects the overall health conditions in the macro-environment. Therefore, examining these patterns can help improve provisions and reduce the number of deaths among both this vulnerable population and society at large."
format: pdf
number-sections: true
bibliography: references.bib 
toc: true

@@

#load necessary package 
library(tidyverse)
library(ggplot2)
library(dplyr)
library(knitr)
library(tidyr)
library(gridExtra)

# load data
Death_data <- read_csv(here::here("data/analysis_data/Num_death_analysis_data.csv"))
AvgAge_data <- read_csv(here::here("data/analysis_data/AvgAge_death_analysis_data.csv"))

```

@@

# Display the table without the 'id' column
kable(AvgAge_data_no_id, 
      col.names = c("Year", "Total Decedents", 
                    "Avg Age of Death (All)", "Male Decedents", 
                    "Avg Age of Death (Male)", "Female Decedents", 
                    "Avg Age of Death (Female)", "Trans/NB/2S Decedents", 
                    "Avg Age of Death (Trans/NB/2S)"))
```

@@

# creating a line graph 
AvgAge_data |> 
  ggplot(aes(x = year, y = total_decedents)) +
  geom_point() +
  geom_line() +
  labs(title = "Total Shelter Residents Decedents from 2007 to 2024", x = "Year", y = "Total Decedents") +
  theme_minimal() +
   theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_x_continuous(breaks = unique(AvgAge_data$year)) +
  scale_y_continuous(breaks = seq(0, max(AvgAge_data$total_decedents), by = 20))

```

@@

# Plot the graph for filtered data
Death_data_filtered |>
  ggplot(aes(x = YearMonth, y = total_decedents, group = 1)) +
  geom_line(color = "black") +
  geom_point(color = "black") +
  scale_x_discrete(breaks = Death_data_filtered$YearMonth[seq(1, nrow(Death_data_filtered), by = 6)]) + 
  labs(title = "Trends in Total Decedents by Month(2019-2023)",
       x = "Month-Year",
       y = "Total Decedents") +
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 8)) + 
  theme(plot.title = element_text(hjust = 0.5))

```
\newpage
@fig-T illustrates the number of deaths among genders. The bar graph clearly shows that the number of male decedents is significantly greater than that of female decedents, a trend consistent across all the years presented. Additionally, the graph indicates that the mortality rate among males is more volatile over the years, particularly from 2019 to 2022. These results may be attributed to the proportion of males living in shelters; further details can be found in @sec-3-dpoint.
```{r}
#| label: fig-T 
#| fig-cap: Total Decedents Split by Gender (Female VS Male)
#| echo: false
#| warning: false
#| message: false

# Reshape the data for plotting
plot_data <- AvgAge_data |>
  select(year, Male_decedents, Female_decedents)|>
  pivot_longer(cols = c(Male_decedents, Female_decedents),
               names_to = "Gender",
               values_to = "Mortality")

@@

# Create the bar graph with adjusted year labels
plot_data |>
  ggplot(aes(x = year_short, y = Mortality, fill = Gender)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
  labs(title = "Mortality Numbers of Male Vs Female Decedents over 2007 to 2024",
       x = "Year (2000s)",
       y = "Number of Decedents") +
  scale_fill_manual(values = c("Male_decedents" = "blue", "Female_decedents" = "pink")) +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = "bottom") +
  theme(plot.title = element_text(hjust = 0.5))

```
@fig-AvgAgeofDecedentsFemaleVSMale further examines the differences in average age at death between females and males. It's important to note that there are significantly more male deaths than female deaths, which could result in a lower average age for males due to the larger sample size. Although the graph does not definitively indicate whether males generally die at an older age than females or vice versa, it does suggest that the average age at death for males appears to be considerably higher than that for females during many periods indicated in the graph. More information is available in @sec-3-dpoint.

@@

# Reshape the data for plotting average age of death
avg_age_data <- AvgAge_data |>
  select(year, Average_age_of_death_male_decedents, Average_age_of_death_female_decedents) %>%
  pivot_longer(cols = c(Average_age_of_death_male_decedents, Average_age_of_death_female_decedents),
               names_to = "Gender",
               values_to = "Average_Age") |>
  mutate(year_short = sprintf("%02d", year %% 100))

# Create the line graph for average age of death
avg_age_data |>
  ggplot(aes(x = year_short, y = Average_Age, color = Gender, group = Gender)) +
  geom_line(size = 1) +   
  geom_point(size = 2) +    
  labs(title = "Average Age of Death for Male Vs Female Decedents",
       x = "Year",
       y = "Average Age of Death") +
  scale_color_manual(values = c("Average_age_of_death_male_decedents" = "blue", 
                                 "Average_age_of_death_female_decedents" = "pink")) +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = "bottom") +
  theme(plot.title = element_text(hjust = 0.5))

```

@@

# Create the bar plots for 2007 and 2008
plot_2007 <- ggplot(current_year_data_2007, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(title = "Total Decedents by Month in 2007", 
       x = "Month", 
       y = "# Decedents") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45))+
  theme(plot.title = element_text(hjust = 0.5, size = 10))

plot_2008 <- ggplot(current_year_data_2008, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(title = "Total Decedents by Month in 2008", 
       x = "Month", 
       y = "# Decedents") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45))+
  theme(plot.title = element_text(hjust = 0.5, size = 10))

plot_2009 <- ggplot(current_year_data_2009, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(title = "Total Decedents by Month in 2009", 
       x = "Month", 
       y = "# Decedents") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

plot_2010 <- ggplot(current_year_data_2010, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(title = "Total Decedents by Month in 2010", 
       x = "Month", 
       y = "# Decedents") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

# Arrange plots side by side
grid.arrange(plot_2007, plot_2008, plot_2009, plot_2010, ncol = 2)

```

@@

# Create the bar plots
plot_2011 <- ggplot(current_year_data_2011, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(title = "Total Decedents by Month in 2011", 
       x = "Month", 
       y = "# Decedents") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

plot_2012 <- ggplot(current_year_data_2012, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(title = "Total Decedents by Month in 2012", 
       x = "Month", 
       y = "# Decedents") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

plot_2013 <- ggplot(current_year_data_2013, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(title = "Total Decedents by Month in 2013", 
       x = "Month", 
       y = "# Decedents") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

plot_2014 <- ggplot(current_year_data_2014, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(title = "Total Decedents by Month in 2014", 
       x = "Month", 
       y = "# Decedents") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

# Arrange plots side by side
grid.arrange(plot_2011, plot_2012, plot_2013, plot_2014, ncol = 2)

```

@@

plot_2015 <- ggplot(current_year_data_2015, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(title = "Total Decedents by Month in 2015", 
       x = "Month", 
       y = "# Decedents") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

plot_2016 <- ggplot(current_year_data_2016, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(title = "Total Decedents by Month in 2016", 
       x = "Month", 
       y = "# Decedents") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

plot_2017 <- ggplot(current_year_data_2017, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(title = "Total Decedents by Month in 2017", 
       x = "Month", 
       y = "# Decedents") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

plot_2018 <- ggplot(current_year_data_2018, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(title = "Total Decedents by Month in 2018", 
       x = "Month", 
       y = "# Decedents") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

# Arrange plots side by side
grid.arrange(plot_2015, plot_2016, plot_2017, plot_2018, ncol = 2)

```

@@

# Create the bar plots
plot_2019 <- ggplot(current_year_data_2019, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(title = "Total Decedents by Month in 2019", 
       x = "Month", 
       y = "# Decedents") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

plot_2020 <- ggplot(current_year_data_2020, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(title = "Total Decedents by Month in 2020", 
       x = "Month", 
       y = "# Decedents") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

plot_2021 <- ggplot(current_year_data_2021, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(title = "Total Decedents by Month in 2021", 
       x = "Month", 
       y = "# Decedents") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

plot_2022 <- ggplot(current_year_data_2022, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(title = "Total Decedents by Month in 2022", 
       x = "Month", 
       y = "# Decedents") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

# Arrange plots side by side
grid.arrange(plot_2019, plot_2020, plot_2021, plot_2022, ncol = 2)

```

@@

# Create the bar plots
plot_2023 <- ggplot(current_year_data_2023, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(title = "Total Decedents by Month in 2023", 
       x = "Month", 
       y = "# Decedents") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

plot_2024 <- ggplot(current_year_data_2024, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(title = "Total Decedents by Month in 2024", 
       x = "Month", 
       y = "# Decedents") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

# Arrange plots side by side
grid.arrange(plot_2023, plot_2024, ncol = 2)

```

>>>>

---
title: "Mortality Trend Among Shelter Residents: Closely Tied To Virus Outbreaks"
author: 
  - Mandy He
thanks: "Code and data are available at: https://open.toronto.ca/dataset/deaths-of-shelter-residents/"
date: Septmeber 27 2024
date-format: long
abstract: "Homelessness remain pressing issues in today’s society, particularly evident in downtown Toronto, these individuals often face severe health issues, leading to an increased risk of mortality. This paper analyzes trends in mortality rates among shelter residents in the City of Toronto from 2007 to 2024, highlighting patterns over time and exploring the factors contributing to these rates. This paper found trend in mortality rate of this minority group reflects the overall health conditions in the macro-environment. Therefore, examining these patterns can help improve provisions and reduce the number of deaths among both this vulnerable population and society at large."
format: pdf
number-sections: true
bibliography: references.bib 
toc: true

@@

# load necessary package
library(tidyverse)
library(ggplot2)
library(dplyr)
library(knitr)
library(tidyr)
library(gridExtra)

# load data
Death_data <- read_csv(here::here("data/analysis_data/Num_death_analysis_data.csv"))
AvgAge_data <- read_csv(here::here("data/analysis_data/AvgAge_death_analysis_data.csv"))
```

@@

# Display the table without the 'id' column
kable(AvgAge_data_no_id,
  col.names = c(
    "Year", "Total Decedents",
    "Avg Age of Death (All)", "Male Decedents",
    "Avg Age of Death (Male)", "Female Decedents",
    "Avg Age of Death (Female)", "Trans/NB/2S Decedents",
    "Avg Age of Death (Trans/NB/2S)"
  )
)
```

@@

# creating a line graph
AvgAge_data |>
  ggplot(aes(x = year, y = total_decedents)) +
  geom_point() +
  geom_line() +
  labs(title = "Total Shelter Residents Decedents from 2007 to 2024", x = "Year", y = "Total Decedents") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = unique(AvgAge_data$year)) +
  scale_y_continuous(breaks = seq(0, max(AvgAge_data$total_decedents), by = 20))
```

@@

# Plot the graph for filtered data
Death_data_filtered |>
  ggplot(aes(x = YearMonth, y = total_decedents, group = 1)) +
  geom_line(color = "black") +
  geom_point(color = "black") +
  scale_x_discrete(breaks = Death_data_filtered$YearMonth[seq(1, nrow(Death_data_filtered), by = 6)]) +
  labs(
    title = "Trends in Total Decedents by Month(2019-2023)",
    x = "Month-Year",
    y = "Total Decedents"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 8)) +
  theme(plot.title = element_text(hjust = 0.5))
```
\newpage
@fig-T illustrates the number of deaths among genders. The bar graph clearly shows that the number of male decedents is significantly greater than that of female decedents, a trend consistent across all the years presented. Additionally, the graph indicates that the mortality rate among males is more volatile over the years, particularly from 2019 to 2022. These results may be attributed to the proportion of males living in shelters; further details can be found in @sec-3-dpoint.
```{r}
#| label: fig-T
#| fig-cap: Total Decedents Split by Gender (Female VS Male)
#| echo: false
#| warning: false
#| message: false

# Reshape the data for plotting
plot_data <- AvgAge_data |>
  select(year, Male_decedents, Female_decedents) |>
  pivot_longer(
    cols = c(Male_decedents, Female_decedents),
    names_to = "Gender",
    values_to = "Mortality"
  )

@@

# Create the bar graph with adjusted year labels
plot_data |>
  ggplot(aes(x = year_short, y = Mortality, fill = Gender)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
  labs(
    title = "Mortality Numbers of Male Vs Female Decedents over 2007 to 2024",
    x = "Year (2000s)",
    y = "Number of Decedents"
  ) +
  scale_fill_manual(values = c("Male_decedents" = "blue", "Female_decedents" = "pink")) +
  theme_minimal() +
  theme(
    legend.title = element_blank(),
    legend.position = "bottom"
  ) +
  theme(plot.title = element_text(hjust = 0.5))
```
@fig-AvgAgeofDecedentsFemaleVSMale further examines the differences in average age at death between females and males. It's important to note that there are significantly more male deaths than female deaths, which could result in a lower average age for males due to the larger sample size. Although the graph does not definitively indicate whether males generally die at an older age than females or vice versa, it does suggest that the average age at death for males appears to be considerably higher than that for females during many periods indicated in the graph. More information is available in @sec-3-dpoint.

@@

# Reshape the data for plotting average age of death
avg_age_data <- AvgAge_data |>
  select(year, Average_age_of_death_male_decedents, Average_age_of_death_female_decedents) %>%
  pivot_longer(
    cols = c(Average_age_of_death_male_decedents, Average_age_of_death_female_decedents),
    names_to = "Gender",
    values_to = "Average_Age"
  ) |>
  mutate(year_short = sprintf("%02d", year %% 100))

# Create the line graph for average age of death
avg_age_data |>
  ggplot(aes(x = year_short, y = Average_Age, color = Gender, group = Gender)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  labs(
    title = "Average Age of Death for Male Vs Female Decedents",
    x = "Year",
    y = "Average Age of Death"
  ) +
  scale_color_manual(values = c(
    "Average_age_of_death_male_decedents" = "blue",
    "Average_age_of_death_female_decedents" = "pink"
  )) +
  theme_minimal() +
  theme(
    legend.title = element_blank(),
    legend.position = "bottom"
  ) +
  theme(plot.title = element_text(hjust = 0.5))
```

@@

# Create the bar plots for 2007 and 2008
plot_2007 <- ggplot(current_year_data_2007, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(
    title = "Total Decedents by Month in 2007",
    x = "Month",
    y = "# Decedents"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

plot_2008 <- ggplot(current_year_data_2008, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(
    title = "Total Decedents by Month in 2008",
    x = "Month",
    y = "# Decedents"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

plot_2009 <- ggplot(current_year_data_2009, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(
    title = "Total Decedents by Month in 2009",
    x = "Month",
    y = "# Decedents"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

plot_2010 <- ggplot(current_year_data_2010, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(
    title = "Total Decedents by Month in 2010",
    x = "Month",
    y = "# Decedents"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

# Arrange plots side by side
grid.arrange(plot_2007, plot_2008, plot_2009, plot_2010, ncol = 2)
```

@@

# Create the bar plots
plot_2011 <- ggplot(current_year_data_2011, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(
    title = "Total Decedents by Month in 2011",
    x = "Month",
    y = "# Decedents"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

plot_2012 <- ggplot(current_year_data_2012, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(
    title = "Total Decedents by Month in 2012",
    x = "Month",
    y = "# Decedents"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

plot_2013 <- ggplot(current_year_data_2013, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(
    title = "Total Decedents by Month in 2013",
    x = "Month",
    y = "# Decedents"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

plot_2014 <- ggplot(current_year_data_2014, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(
    title = "Total Decedents by Month in 2014",
    x = "Month",
    y = "# Decedents"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

# Arrange plots side by side
grid.arrange(plot_2011, plot_2012, plot_2013, plot_2014, ncol = 2)
```

@@

plot_2015 <- ggplot(current_year_data_2015, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(
    title = "Total Decedents by Month in 2015",
    x = "Month",
    y = "# Decedents"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

plot_2016 <- ggplot(current_year_data_2016, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(
    title = "Total Decedents by Month in 2016",
    x = "Month",
    y = "# Decedents"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

plot_2017 <- ggplot(current_year_data_2017, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(
    title = "Total Decedents by Month in 2017",
    x = "Month",
    y = "# Decedents"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

plot_2018 <- ggplot(current_year_data_2018, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(
    title = "Total Decedents by Month in 2018",
    x = "Month",
    y = "# Decedents"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

# Arrange plots side by side
grid.arrange(plot_2015, plot_2016, plot_2017, plot_2018, ncol = 2)
```

@@

# Create the bar plots
plot_2019 <- ggplot(current_year_data_2019, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(
    title = "Total Decedents by Month in 2019",
    x = "Month",
    y = "# Decedents"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

plot_2020 <- ggplot(current_year_data_2020, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(
    title = "Total Decedents by Month in 2020",
    x = "Month",
    y = "# Decedents"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

plot_2021 <- ggplot(current_year_data_2021, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(
    title = "Total Decedents by Month in 2021",
    x = "Month",
    y = "# Decedents"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

plot_2022 <- ggplot(current_year_data_2022, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(
    title = "Total Decedents by Month in 2022",
    x = "Month",
    y = "# Decedents"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

# Arrange plots side by side
grid.arrange(plot_2019, plot_2020, plot_2021, plot_2022, ncol = 2)
```

@@

# Create the bar plots
plot_2023 <- ggplot(current_year_data_2023, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(
    title = "Total Decedents by Month in 2023",
    x = "Month",
    y = "# Decedents"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

plot_2024 <- ggplot(current_year_data_2024, aes(x = month, y = total_decedents)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(
    title = "Total Decedents by Month in 2024",
    x = "Month",
    y = "# Decedents"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

# Arrange plots side by side
grid.arrange(plot_2023, plot_2024, ncol = 2)
```
